---
output: html_document
---

##QuBBD Figure Generation

###Dataset Description 

| Gleason Grade | Image Count   |  Dimensions
| :-----------: |:-------------:| :----------:
| Grade 3 | 19 | 1100 x 1100
| Grade 4 | 48 | 1100 x 1100
| Grade 5 | 12 | 1100 x 1100

###Preprocessing
```{r, cache=TRUE}
rm(list=ls())
library(doParallel)
library(foreach)
library(stringr)
library(TDA)
library(cluster)
library(ggplot2)
library(gplots)
no_cores <- detectCores()
setwd("~/Documents/Lawson_Research/")
nuclei<-read.csv("./ProstateTDA/data/2016-09-14/grant1100sub.csv")
nuclei$Metadata_FileLocation<-gsub(".*\\_(.*)\\..*","\\1",nuclei$Metadata_FileLocation)
meta<-unique(nuclei$Metadata_FileLocation)
nucleisplit<-split(nuclei, nuclei$Metadata_FileLocation)
gleason<-str_extract(meta, "(?<=g)[0-9]")
```

###Generate Persistence Diagrams
```{r, cache=TRUE}
Diag<-list()
cl<-makeCluster(no_cores)
registerDoParallel(cl)
strt<-Sys.time()
Diag<-foreach(i=nucleisplit, .packages='TDA') %dopar%
{
  xnuc<-i$Location_Center_X
  ynuc<-i$Location_Center_Y
  X<-matrix(c(i$Location_Center_X,i$Location_Center_Y),ncol=2)
  xlim<-c(0,max(xnuc))
  ylim<-c(0,max(ynuc))
  grid<-3
  gridDiag( X=X, FUN=dtm, m0=.01, lim=cbind(xlim,ylim), location=TRUE, by=grid, sublevel=T, library="Dionysus", printProgress=FALSE )
}
print(Sys.time()-strt)
stopCluster(cl)
```

###Compute Pairwise Bottleneck Distance
```{r, fig.height=9, fig.width=9, cache=TRUE}
no_cores <- detectCores()
cl<-makeCluster(no_cores)
registerDoParallel(cl)
strt<-Sys.time()

bottleneck<-foreach(i = 1:length(Diag), .packages='TDA', .combine=cbind) %:% foreach(j= 1:length(Diag), .packages='TDA', .combine=c) %dopar% {
    bottleneck(Diag[[i]][[1]],Diag[[j]][[1]], dimension=1)
}
print(Sys.time()-strt)
stopCluster(cl)
colnames(bottleneck)<-gleason
rownames(bottleneck)<-gleason
distance = dist(bottleneck, method = "manhattan")
cluster = hclust(distance, method = "ward.D")
heatmap.2(bottleneck,
  Rowv = as.dendrogram(cluster), # apply default clustering method
  Colv = as.dendrogram(cluster) # apply default clustering method
)
```

###Compute Pairwise Wasserstein Distance
```{r, fig.height=9, fig.width=9}
cl<-makeCluster(no_cores)
registerDoParallel(cl)
strt<-Sys.time()

wasserstein<-foreach(i = 1:length(Diag), .packages='TDA', .combine=cbind) %:% foreach(j= 1:length(Diag), .packages='TDA', .combine=c) %dopar% {
    wasserstein(Diag[[i]][[1]],Diag[[j]][[1]], dimension=1)
}
print(Sys.time()-strt)
stopCluster(cl)
colnames(wasserstein)<-gleason
rownames(wasserstein)<-gleason
distance = dist(wasserstein, method = "manhattan")
cluster = hclust(distance, method = "ward.D")
heatmap.2(wasserstein,
  Rowv = as.dendrogram(cluster), # apply default clustering method
  Colv = as.dendrogram(cluster) # apply default clustering method
)
heatmap.2(wasserstein,
  Rowv = gleason, # apply default clustering method
  Colv = gleason # apply default clustering method
)

row<-wasserstein[order(rownames(wasserstein)),]
col<-row[,order(colnames(wasserstein))]
heatmap.2(col, Rowv=FALSE, Colv=FALSE)
```

###Bottleneck Cluster Dendrogram
```{r,fig.height=9, fig.width=9, cache=TRUE}
plot(hclust(dist(bottleneck), method="single"), axes=FALSE, ylab='', xlab='', main=NULL)
```
###Wasserstein Cluster Dendrogram
```{r,fig.height=9, fig.width=9, cache=TRUE}
plot(hclust(dist(wasserstein), method="single"), axes=FALSE, ylab='', xlab='', main=NULL)
```
###Multidimensional Scaling
```{r,fig.height=9, fig.width=9, cache=TRUE}
d <- dist(bottleneck) 
fit <- cmdscale(d,eig=TRUE, k=2) # k is the number of dim
x <- fit$points[,1]
y <- fit$points[,2]
plot(x, y, main="Bottleneck",	type="n")
text(x, y, labels = row.names(bottleneck), cex=.7, col=gleason)

d <- dist(wasserstein)
fit <- cmdscale(d,eig=TRUE, k=2) # k is the number of dim
x <- fit$points[,1]
y <- fit$points[,2]
plot(x, y, main="Wasserstein",	type="n")
text(x, y, labels = row.names(wasserstein), cex=.7, col=gleason)
```

###K-Means Clustering
```{r, fig.height=9, fig.width=9, cache=TRUE}
fitBot<-kmeans(bottleneck, 5)
fitWas<-kmeans(wasserstein, 5)
clusplot(bottleneck, fitBot$cluster, color=TRUE, shade=TRUE, 
  	labels=2, lines=0)
clusplot(wasserstein, fitWas$cluster, color=TRUE, shade=TRUE, 
  	labels=2, lines=0)
